Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-21 2015-turklang-kazdep/paper.tex
some table examples
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60932 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{table}[htbp]
	\centering
	\caption{The default (first line of each) and ``zero-derived'' uses of nominals, adjectives, and adverbs}\label{tab:zeroderiv}
	\begin{tabular}{lp{8em}p{22em}}
		\toprule
			\textbf{Category} & \textbf{Function} & \textbf{Example} \\
		\midrule
			Nominals & Substantive\newline
							Attributive\newline
							Adverbial
						& hargle\newline 
							jargal\newline
							бір рет \gloss{once} \\
			Adjectives & Attributive\newline
							Substantive\newline
							Adverbial
						& \kazakh{\textbf{жақсы} үй} \gloss{nice house} \newline
						\kazakh{ең \textbf{жақсы}лары} \gloss{\textbf{the nice}st \textbf{ones}} \newline
						\kazakh{оны \textbf{жақсы} танимын} \gloss{I know him/her \textbf{well}.}
						\\
			Adverbs & Adverbial
						& 
						\\
		\bottomrule
	\end{tabular}

>>>>

\begin{table}[htbp]
	\centering
	\caption{The default (first line of each) and ``zero-derived'' uses of nominals, adjectives, and adverbs}\label{tab:zeroderiv}
	\begin{tabular}{lp{5em}p{22em}}
		\toprule
			\textbf{Category} & \textbf{Function} & \textbf{Example} \\
		\midrule
			Nominals & Substantive\newline
							Attributive\newline
							Adverbial
						& \kazakh{\textbf{Қонақ}тарымыз бай.} \gloss{Our \textbf{guest}s are rich.}\newline 
							\kazakh{\textbf{қонақ} үй} \gloss{hotel (lit., \textbf{guest} house)}\newline
							\kazakh{бір \textbf{рет}} \gloss{one \textbf{time}} \\
			Adjectives & Attributive\newline
							Substantive\newline
							Adverbial
						& \kazakh{\textbf{жақсы} үй} \gloss{\textbf{nice} house} \newline
						\kazakh{ең \textbf{жақсы}лары} \gloss{\textbf{the nice}st \textbf{ones}} \newline
						\kazakh{Оны \textbf{жақсы} танимын.} \gloss{I know him/her \textbf{well}.}
						\\
			Adverbs & Adverbial
						& \kazakh{Ол \textbf{кеше} кетті} \gloss{S/he left \textbf{yesterday}.}
						\\
		\bottomrule
	\end{tabular}
